\documentclass{exam}
\usepackage{../../scripts/meta}

%%% Change these %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\discnumber{4}
\title{}
\date{Berlekamp-Welsh, Countability, Self Reference, Counting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\rule{\textwidth}{0.15em}
\fontsize{12}{15}\selectfont
\thispagestyle{empty}


%%% General Notes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{General Comments}
\begin{questions}
  \item Counting: 1.1
    \begin{itemize}
      \item Make sure to give a general intro on stars \& bars problems, so that students can gain intuition on how to convert problems they see into stars \& bars. 
      \item Ensure that students understand (in)distinguishable balls/(in)distinguishable bins. Like stars \& bars, students should be able to understand what problems correspond to balls \& bins/stars \& bars, etc.
      \item Only do extra problems if you have time
      \item Feel free to just skim over theorems
    \end{itemize}
  \item Combinatorial Proofs: \#1, 2, 3
  \item Discrete Probability: \#1 (very basic for later in the week people)
    \begin{itemize}
      \item Disjoint vs Independent. The easiest way to emphasize this difference is through the venn diagrams above (disjoint events are almost always DEPENDENT).
      \item Uniform probability space and how to calculate probabilities using set sizes in that space.
      \item Feel free to come up with your own probability space problems. If students are shaky on the concepts, I recommend the following problems (only the solutions are below, but you can guess what the questions were.. Walrand seems to llike these divide-up-your-outcome-space problems
      \item For problems on worksheet, just need to know that there are exactly 4 Kings in a deck of cards
            Also, for each add that you are drawing exactly 2 cards in the manner described
    \end{itemize}
  \item Conditional Probability
    \begin{itemize}
      \item Oski (the last problem) is a more involved one, which you may want to recommend that students do on there own, as it is a good exam-prep-style problem.
      \item You may need to spend more time on the mutual independence question as it requires students to generate an example, and pair-wise/mutual independence is not always well understood.
      \item Most of the other problems should be more straightforward.
    \end{itemize}
\end{questions}

\section{Questions}


\end{document}
